Buildtime Trend : What's trending in your build process

### 2015-03-29 buildtimetrend/presentation.tex
mention JSON
add demo

      \item A payload with build data is sent

@@

>>>>

      \item A JSON payload with build data is sent

@@

    \frametitle{Demo}
      \item Service : \href{https://buildtimetrend.herokuapp.com/}{\small{https://buildtimetrend.herokuapp.com/}}
      \item Dashboard : \href{https://buildtimetrend.herokuapp.com/dashboard/buildtimetrend/python-lib/index.html}{\small{https://buildtimetrend.herokuapp.com/dashboard/buildtimetrend/python-lib}}
      \item Badges : \href{https://github.com/buildtimetrend/service\#badge-examples}{\small{https://github.com/buildtimetrend/service\#badge-examples}}
